paper1_figures

### 2023-11-15 scoping_review_short.Rmd
15.11

@@

Five individual factors that can impact cooperation emerged from the litterature review: gender, social status, group identification, values and personality traits, and trust. In the following sections, the principal effects of these factors on cooperation are described. Moreover, an overview of the moderators of each effect is provided. More details about moderators are included in the Appendix A.

@@

Lastly, gender differences are also linked to social status, with women representing the low-status group [@Sell2009]. Therefore, gender differences in cooperation could also be partly explained by social status: to have a better understanding of this hypothesis, it is important to gain insights on how social status impact cooperation.

@@

Cooperation can be modified by introducing incentives, who can be either punishments or rewards[^1]. In the literature, punishment has received a greater attention than reward [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation has been widely demonstrated. In fact, when participants can punish other members for not contributing equally cooperation is higher than when this is not possible [e.g. @Balliet2011a; @Pfattheicher2018]. Moreover, the presence of a punishment system increases the perception of fairness [@Nockur2021].

[^1]: Since the interest of the present review is to investigate how the internal organization of a group can affect cooperation, only papers that studied situations where the participants could give rewards or punishments to each-others are included. Incentives given by third party have also an effect on cooperation, but they are not included in this review.

@@

At the same time, punishment must be applied with carefulness. For instance, the most successful groups are those who punish with caution and not in early stages of the interaction, and who have a norm of when and how punishment should be applied [@Rockenbach2019]. Moreover, punishment has also two negative sides. First, it could entails a second-order social dilemma, since cooperative participants can free-ride on the effort of other cooperators who punish non-cooperators [@Milinski2012]. Secondly, when all participants can punish independently of their contributions, anti-social punishment (i.e. the punishment of cooperators by non-cooperators) can arise [@Xiao2016]. A solution could be to implement a system of democratic punishment, where a fine is given only if a majority of participants agree. In fact, with this kind of system the punishment level is lower, while final payoff and cooperation rates are higher [@Pfattheicher2018].

On the other side, rewarding systems are less investigated. Generally, they have a positive effect on cooperation [@Balliet2011a], but it is not clear whether they are more efficient than punishment [as found by @Chen2022], less efficient [see @Milinski2012] or equivalent [see @Balliet2011a]. Similarly to punishments, rewards have a stronger effect if their implementation is costly and during iterated, rather than single, interactions [@Balliet2011a].

To conclude, incentives can enhance cooperation, but they have some negative sides. First, they reduce participants' intrinsic motivation to cooperate [@VanDijk2015; @Schlosser2018] by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009]. Secondly, incentives undermine participants' trust in other members' internal motivation to cooperate. Therefore, if they are removed, cooperation drops [@Irwin2014; @Mulder2006].

@@

>>>>

During last years, the interest in alternative ways of social organization increased drastically because of the social and ecological crises we are facing [@Euler2018]. Commons are one of these alternatives, since they are a way of organizing resources not involving the classic private and public model [@Ostrom1990], and, therefore, they represent an option to the capitalistic system [@Euler2019]. For this reason, commons could be the needed change to attain a more sustainable and fair social organization [@Seravalli2018].

Commons have been defined in different ways, starting by Elinor Ostrom who, in her seminal work, refers to them as a resource system shared between a self-managed community of users [@Ostrom1990]. This community has a set of social practices, values and norms. Therefore, it is important to consider the commons not only as a resource, but as the integration of the resource, the community and its social protocols [@Bollier2014]. For this reason, beyond the material aspect, the notion of social practices (i.e. commoning) is essential [@Euler2018]. "Commoning" refers to the process through which people (i.e. the commoners) find solutions for their needs by self-organizing independently from the state or the market, and by creating autonomously managed institutions to govern the shared resource [@Euler2018; @Schmelzer2022]. The community is therefore engaged in defining rules to successfully manage the commons [@Meroni2022]. In conclusion, commons can be understood as "living social systems" who allow commoners to self-organize to address shared problems [@Bollier2019].

These definitions highlight the importance of the community as a part of the commons, and that is why it is essential to have a closer look to the people who form it. More specifically, in order for a commons[^1] to be successful, its members have to cooperate, i.e to incur a personal sacrifice for the greater good [@Kollock1998]. Although its importance, cooperation can be difficult to achieve due to two characteristics of the commons' social dynamic. First, people can believe that their individual contribution will not have a big impact, and this feeling of personal inefficacy discourages cooperation [@VanVugt1998]. Secondly, in a commons, every member faces a conflict between individual, short-term interests and collective, long-term ones [@Hardin1968]. Act for the common good requires a personal sacrifice, and therefore the temptation to pursue the individual interest is constantly present. For these reasons, it is essential to understand how cooperation in commons can be improved, and which factors impact it.

[^1]: The term "commons" is both singular and plural [@Bollier2014]. For the difference between the singular forms "common" and "commons", see @Feinberg2021.

## Cooperating in commons

In the existing literature, there are several explications of why people adopt or not cooperative behaviours in commons. For instance, the Rational Choice Theory predicts that people are too self-interested to cooperate in such contexts. As a consequence, they will inevitably destroy the shared resource, unless an external institution forces them to cooperate [@DeCaro2021; @Hardin1968]. However, there are some less pessimistic theories that predict that people can transcend their personal interest and successfully cooperate in commons. An example is the Greed Efficiency Fairness hypothesis, which posits that the individuals' greed to pursue their narrow interests is constrained by their desire to use the resource efficiently and to fairly allocate it between members [@Wilke1991]. Similarly, according to the Humanistic Rational Choice Theory, the desire to maintain basic social-psychological needs motivates people to cooperate [@DeCaro2021]. Finally, cooperating in commons can also be a self-presentation strategy [@VanVugt2010a], since showing altruistic behaviours has a positive effect on reputation [@Roberts1998].

On a more practical level, @Ostrom1990 reported several cases of successful commons, where individuals managed to create a system to ensure cooperation. Based on her observations, she established eight design principles that distinguish successful from unsuccessful commons. First, commons need clearly defined boundaries to determine who has access to the shared resource, and the governing rules must take into account the local conditions. Moreover, people affected by these rules must be able to participate in modifying them. A monitoring and a graduated sanctions system must also be implemented, as well as low-cost conflict resolution arena. Finally, external authorities must not challenge the commons' members' right to self-organize[^2] [@Ostrom1990].

[^2]: The last principle is valid only for commons that are part of a larger system, and is about nested enterprises: all the governance activities should be organized in multiple layers of nested enterprises.

There are therefore several studies that focused on commons and on how they can be successful, but social psychological and quantitative perspectives are missing from this literature. In fact, to the authors' knowledge, there are few or no studies that investigated the causal effect of individual and group factors on people's willingness to cooperate in a real-life commons.

At the same time, this approach is very popular in the laboratory study of social dilemmas, which allowed to identify several factors that shape cooperation [e.g. @VanLange2013]. In this experiments, people face a conflict between personal and collective interest: each individual obtains a higher personal payoff with a non-cooperative, self-interested behaviour than with a social, cooperative one, independently from what others do. At the same time, everybody's payoff is higher if all cooperate than if all defect [@Dawes1980]. Since many of the current global problems have a social dilemma structure, this topic has been extensively studied in different fields such as psychology, economy, biology, or mathematics [@VanLange2013]. Thanks to their easy implementation in a laboratory, social dilemmas are very useful to gain insights into how cooperation works, because they provide a standard experimental paradigm to test under which conditions people cooperate [@Balliet2011].

## Current review

Commons and social dilemmas are deeply linked. First, they share the same basic conflict between personal and collective interests [@Hardin1968; @Dawes1980]. For this reason, commons can be considered as a particular case of social dilemma. In fact, @Kopelman2002 used the term of "commons dilemma" to define situations where a non cooperative behaviour can seriously endanger the future of the shared resource. Moreover, commons have been classified by @Cumming2018 as "take-some dilemmas", a specific kind of social dilemma where people are tempted to increase their personal benefit by taking more than their fair share from a shared resource. Moreover, cooperation and defection in social dilemma laboratory experiments can predict people's behaviour in a real-life commons [e.g. @Reindl2019].

The aim of the current paper is to synthesize the existing researches about cooperation in social dilemmas, to provide a set of factors that could impact cooperative behaviours in commons. This work will therefore lay the foundations to implement experimental and quantitative studies in real-life commons, which, in turn, will allow to gain insights about cooperation in this context. Other studies already used a social dilemma framework to study real-life commons [e.g. @Hartl2022]. While these studies usually focused on just one particular case, the current review is seeking to extend this approach by using social dilemma literature to gain a global understanding of cooperation in commons.

This scoping review has two main goals. The first is to identify individual factors that can shape cooperation in commons. In fact, taking into account the specific community and commoners is essential to fully understand a commons' functioning [@Dove2019]. Moreover, since it has been widely demonstrated that commoners can successfully self-organize to govern a commons [@Ostrom1990; @Larsson2016], the second goal is to understand which strategies groups can implement to encourage their members to cooperate.

# Methods

To conduct this scoping review, different scientific publications were analyzed in response to the research questions. To gather the papers, we performed a Boolean search methodology in Scopus, Web of Science and ScienceDirect. The main key phrases were "social dilemma", "public good", "common resource", and "commons", and each of them was paired with each one of the following: "cooperation", "conflicts", "reciprocity", and "trust". The research was made during the month of August, 2023. According to @Munn2022, the type of source was not a selection criterion, therefore journal articles, conference papers and book chapters could be included, to have an idea as complete as possible about the existing literature on the topic. Moreover, there were not any chronological or geographical limitations, once again to provide a broader vision. There were however some selection criteria concerning the papers' methodology. First, only papers written in English were selected. Moreover, human participants were needed, so studies of social dilemmas through an agent-based model were excluded. Secondly, among experimental or correlative studies, only cases with adult participants were selected.

Initially, 5210 papers emerged from the key phrases search. Deleting the duplicates reduced them to 4586. Based on titles and abstracts, 4333 articles were eliminated, leaving 253 texts to examine. After a full-text evaluation of the remaining papers, 89 were selected for the present review. Figure 1 resumes this selection process.

## Papers' description

The 89 included papers were published between 1984 and 2023, with a median of 2015. Almost all of the selected texts were journal articles, with the only exception being a book chapter. Most of them were experimental studies (*N*=60), followed by literature review and meta-analysis (*N*=14) and correlative studies[^3] (*N*=14). The remaining paper was a qualitative study.

[^3]: Studies where at least one variable is manipulated by researchers are part of the category "experimental studies", while "correlative studies" refers to papers using quantitative analysis, but without manipulations.

### Topic

The papers' topic were in four categories: first, "lab-based social dilemma" (*N*=75) refers to highly controlled laboratory experiments where participants had to take cooperative decision. The second category is "real-life social dilemma" (*N*=7), and investigated cooperation in different real-life situations with a social dilemma structure such as recycling behaviours [@Rompf2017] or use of public transportation [@VanLange1998]. Thirdly, papers in the category "lab-based commons" (*N*=3) used a laboratory social dilemma paradigm, but with clear references to a concrete common. For instance, in @Mosler1993, participants had to imagine to be fishermen who shared a common basin. Finally, "real-life commons" (*N*=4) refers to papers who studied cooperation with participants that were members of a commons in their everyday life.

### Journal

Most of the papers concerned psychology and economy. In fact, more than a half was published in psychology journals, such as *Group Processes & Integroup Relations* or *Psychological Bulletin* (*N*=34), in economic journals like *Experimental Economics* (*N*=14), or in interdisciplinary ones such as *Journal of Economic Psychology* (*N*=8).

### Country

Finally, most of the studies were conducted in Europe (*N*=40) (especially in Germany (*N*=12) and in the Netherlands (*N*=8)), followed by North America (*N*=20, of which *N*=19 in the USA) and Asia (*N*=7, of which *N*=6 in China). Moreover, six studies were set in more than one country, and fourteen were meta-analysis or literature reviews. The two remaining studies took place in Australia and in Colombia, respectively.

A resume of the papers' description is provided in Table 1.

@@

Five individual factors that can impact cooperation emerged from the literature review: gender, social status, group identification, values and personality traits, and trust. In the following sections, their principal effects on cooperation are described. Moreover, an overview of the moderators of each effect is provided. More details about moderators are included in the Appendix A.

@@

Lastly, gender is also linked to social status, with women representing the low-status group [@Sell2009]. Therefore, gender differences in cooperation could also be partly explained by social status: to have a better understanding of this hypothesis, it is important to gain insights on how social status impacts cooperation.

@@

Cooperation can be modified by introducing incentive systems, that can be either punishments or rewards. In the literature, punishment has received a greater attention [@Balliet2011a; @VanDijk2015], and its positive effect on cooperation has been widely demonstrated. In fact, when participants can punish other members for not contributing equally, cooperation and the perceived fairness are higher [@Pfattheicher2018; @Nockur2021].

@@

At the same time, punishment must be applied with carefulness. Ideally, groups should not punish in early stages of the interaction, and have a norm of when and how punishment must be applied [@Rockenbach2019]. Moreover, punishment could entails a second-order social dilemma, since cooperators are better-off by non punishing, if all others do [@Milinski2012]. Also, if there are no rules on who can punish, non-cooperators can punish cooperators as a form of retaliation [@Xiao2016; @VanDijk2015]. A democratic punishment system, where a fine is given only if a majority agree, could solve these problems [@Pfattheicher2018].

On the other side, rewarding systems are less investigated. Generally, they have a positive effect on cooperation [@Balliet2011a], but it is not clear whether they are more efficient than punishment [see @Chen2022], less efficient [see @Milinski2012] or equivalent [see @Balliet2011a]. Rewards have a stronger effect if their implementation is costly and during iterated, rather than single, interactions [@Balliet2011a].

In general, even if they enhance cooperation, incentives have negative sides: they reduce participants' intrinsic motivation to cooperate [@VanDijk2015; @Schlosser2018] by framing the situation as an economic, rather than ethical, dilemma [@VanVugt2009]. They also undermine participants' trust in other members' internal motivation to cooperate. Therefore, if they are removed, cooperation drops [@Irwin2014; @Mulder2006].

@@

The aim of the present paper was to synthesize the existing literature about cooperation in social dilemmas, to identify factors that could impact cooperative behaviours in commons. Through a scoping review approach, we identified nine factors, both at the individual and group level. Our results seem to be in line with others findings about cooperation in commons. For instance, factors such as gender, social status, SVO, incentives, and communication were also found by @Kopelman2002 in their review about lab-based commons, and their effects were the same as the ones reported in the current paper.

Moreover, some of the factors can be related to Ostrom's principles to successfully manage a common resource [@Ostrom1990]. For instance, the clearly defined boundaries can strengthen commoners' social identification, since only when an in- and an out-group exist social identity is salient and therefore an identification is possible [@Tajfel1974]. Even if Ostrom developed this principle on a more organizational level, its secondary effect of creating a social identity can also contribute to improve cooperation. Secondly, communication is essential for the commoners to shape social norms [@Bicchieri2002] and to resolve conflicts. Finally, the principles about the monitoring and the graduated sanction systems underline the importance of incentives. The monitoring system refers to social incentives, and is linked to anonymity, since if people know that their behaviour can be observed, they are more willing to conform to social norms because they worry about others' approval [@Nelissen2013; @Rege2004]. On the other hand, a sanction system can also have a positive impact on cooperation [@Balliet2011a], especially if it is graduate, so if sanctions are not too high at the first violation [@Rockenbach2019].[^4]

[^4]: Principles 2, 7 and 8 refer to elements that are not pertinent to the current review, and therefore do not match any of the factors identified.

Ostrom's principles are especially related to factors at the organizational level. This is understandable when considering her economic approach to the study of the commons. However, taking into account the social dynamics and the characteristics of the commoners is also essential to have a better understanding of how these communities work [@Euler2018; @Nightingale2011]. For this reason, this paper made a step further and identified some individual characteristics affecting the efficiency of commons. Although less studied in commons literature, these individual factors are consistent with existing theories.

First, the reported positive effects of trust on cooperation can be explained through the principle of reciprocity, that posits that individuals cooperate more facing cooperative partners [@Fehr2002; @VanLange1999]. Since in real-life situations it is not always possible to know exactly others' contributions, trust (i.e. beliefs about how much others cooperate) becomes essential to decide how to behave [@Vuolevi2012]. Moreover, trust among participants of a common-pool setting is at core of the framework of @Poteete2010, aimed at explaining why commons can be successful.

Secondly, the influence of SVO on cooperation is explained by the difference between pro-social and pro-self in the importance accorded to the relative benefits. More specifically, pro-social value more others' outcome and equality in outcomes than pro-self [@VanLange1999]. Moreover, the difference in weights accorded to the personal and others' outcome seem to be the only dissimilarity between pro-social and pro-self, because they process the cooperative interaction in the same way [@Fiedler2013].

The reviewed results did not provide a clear conclusion about gender effect on cooperation. However, existing theories would predict that women cooperate more than men, because, according to gender stereotypes, women are more communal and caring, while men are more agentic and performance-oriented [@Eagly2012]. In fact, while managing a natural resource, groups partly composed by women display more solidarity and collaboration than all-men groups [@Westermann2005]. However, every experimental paradigm can trigger the participants' gender identity differently [@Sell2009], and for this reason this effect is subjected to several moderators.

Concerning social status, the analyzed studies showed that usually members of low-status groups cooperated more and showed more solidarity with others low-status members than high-status. Although this effect has not been extensively studied, these results seem to be consistent with the existing literature on social status. First, there are structural differences between high- and low-status group's dynamic, and this makes high-status members more individualistic than low-status [@Lorenzi-Cioldi2002]. High-status individuals also display more system justification and more Social Dominance Orientation than low-status [@Caricati2012; @Vargas-Salfate2018]: they see the social system as fair and they have a preference for inequality between social groups. This is negatively correlated with concern about others and altruism [@Pratto1994].

The last individual factor was group identification, and the reviewed results showed that the more individuals identify with their group, the more they are likely to act for the group's good. In fact, according to the Social Identity Theory, people's identity is also composed by their group affiliations, and the stronger they identify with a social group, the more important this group becomes for their identity and the more their personal interests aligns with group's ones [@Tajfel1974]. Also, within a social group, individuals perceive themselves as more similar to other members, and therefore they are more susceptible to adopt collective goals and behaviours [@Turner1984; @Fritsche2018]. Moreover, strongly identified people are less likely to leave a group in case of failure or difficulties [@Ellemers1997]. Thus, a strong identification is essential for a group's success. In-group identification is also essential to engage in collective actions [@VanZomeren2008], and it is the main predictor of pro-environmental actions in the Social Identity Model of Pro-Environmental Action [SIMPEA, @Fritsche2018].

## Factors' interactions

Until now, the identified factors has been discussed separately. However, their impacts are interconnected, as already anticipated in some reviewed results about moderation effects.

For instance, there are gender differences in trust and SVO: trust is a better predictor of cooperation in women than in men [@Irwin2015; @Dorrough2019], and women are more prevalent between pro-social and less between pro-self [@VanLange1999]. Moreover, SVO and trust are linked [@Ackermann2019], and the expectancy about others' cooperation can even be seen as a part of the construct of SVO [@Bogaert2008]. Therefore, pro-self individuals show less cooperation in part because they expect others not to cooperate.

Trust also depends on social status: high-status individuals display more generalized trust (i.e. general beliefs on others' benevolence), while low-status more depersonalized trust (i.e. more trust in other members of their in-group, just because of their membership) [@Navarro-Carrillo2018]. Since high-status individuals perceive the system as fair [@Caricati2012], it is easier for them to believe in others' benevolent intentions. Conversely, belonging to the group is more important for low-status than for high-status [@Lorenzi-Cioldi2002], therefore they see other group members as more trustworthy, even without knowing them personally.

\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ OK \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_

Secondly, communication impacts several other factors. For instance, it plays an essential role in shaping social norms [@Hogg2006; @Bicchieri2002] and it can improve cooperation by signalling a person's intentions and trustworthiness [@Janssen2015]. Moreover, in a study about organizations, communication was a strong predictor of commitment, that is a component of group identification. This link was especially present for vertical communication, i.e. exchanges about organizational strategies between members at different level of the hierarchy [@Postmes2001]. Therefore, having the opportunity to communicate about the strategies that need to be implemented improve one's identification with the group.

Another factor that influences others is group identification. First, as a consequence of the Social Identity Theory, people who strongly identify with their group are more willing to comply to the group's norms and to pursuit the group's goals [@Tajfel1974]. Therefore, high-identified members need less cooperation-enhancing measures. For instance, incentives are more useful to improve cooperation of low-, rather than high-identified, group members [@VanVugt2009], because high-identified members are already motivated to cooperate. Similarly, given their stronger willingness to act for the group's good, high-identified individuals cooperate even in an anonymous condition, while low-identified acted more for the group goal if their actions were accountable [@Barreto2000].

As already mentioned in the results section, anonymity underlies several other factors. First, when actions are accountable, people are more concerned about others' approval and therefore show more conformity to social norms [@Nelissen2013; @Rege2004]. Also, in large groups [where, as a consequence of the group size, levels of anonymity are higher, @Romano2016] it is more difficult to evaluate the trustworthiness of other participants than in small ones [@Janssen2015].

Finally, economic incentives can have a negative impact on people's internal motivation to cooperate, because they change the perception of the context from ethical to economic [@Janssen2015; @VanVugt2009]. Therefore, even if incentives such as punishments or rewards can be useful to improve cooperation, they reduce the impact of the other factors. For instance, when incentives are present, people think that others cooperate because of them, and this leads to reduced levels of trust [@Irwin2014].

incentives =\> social rewards work better when identifying in the group that can dis-/approve the behaviour @Kopelman2002

##

-   theoretical implications?

Moreover, the analyzed papers showed that people often cooperate. This contradicts the Rational Choice Theory (RCT), who posits that individuals are too self interested to sacrifice their personal benefit to the greater good, unless if forced to do so. Our results are consistent with the existing literature, since RCT has already been refuted by experimental studies, who demonstrated that cooperation was higher than predicted in social dilemmas, and that it was impacted by variables that should not play a role according to RCT [@Ostrom1998].

This review also confirmed the lack of quantitative studies about cooperation in real-life commons: of the 89 analyzed papers, just three had these characteristics, and they all were correlative. Therefore, they could not draw a causal link between the investigated factors and cooperative behaviours.

=\> say that this is a confirmation of a gaps in the literature that should be filled with future researches

-   practical implications: This work will therefore lay the foundations to implement experimental and quantitative studies in real-life commons, which, in turn, will allow to gain insights about cooperation in this context =\> rephrase!

-   In summary, this review has practical implications and can be used as a guide for commons members to design campaigns or activities to improve cooperation. In fact, some of the identified factors can be manipulated in order to create better conditions for cooperation to arise. Moreover, since the different elements are linked, they can impact cooperation both directly and indirectly, via mediation and moderation effects. Based on the consensus of the results and on the quantity of connections with other elements, the factors that seem to have a stronger effect are trust, communication, group identification and accountability of actions. Therefore, interventions based on this elements can be very powerful tools to improve cooperation in commons. On the other hand, some individual factor cannot be manipulated, but must be taken into account when designing an intervention. For instance, commons' composition in terms of gender and social status can have a large influence on the overall cooperation.

# Limitations, future perspectives and conclusion

To conclude, this review summarized existing researches about cooperation in social dilemmas, and therefore provided a set of factors that can help better understanding cooperative behaviours in commons. Moreover, it also highlighted a lack of quantitative studies of this topic in real-life commons. However, this scoping review has also several limitations.

First, there is a lack of representation of the global population. In fact, two thirds of the analyzed papers were studies conducted in Europe or in North America, and the fourteen reviews included were also mostly based on studies from Global North. The current results apply therefore to Western societies and should not be generalized to Global South. In fact, there are cultural differences in individualism and collectivism: generally, North American and European cultures are more individualistic, while South American, African and Asian ones are more collective [@Triandis1989]. These differences affect the extent to which individuals define themselves as part of a group [@Trafimow1991] and, consequently, their behavior in cooperative situations [e.g. @Kuwabara2014]. It is therefore likely that cooperation relies on different mechanisms in Global South and North: comparative studies between this two regions should be conducted in order to reach a global understanding of cooperation.

Moreover, although the aim was to use results of social dilemma researches to gain a better understanding of commons, most of the included studies had a laboratory setting. Such a simplification of real-life situations do not allow to exactly reproduce the dynamics present in a commons [@Henry2011; @Cole2010]. In fact, some elements such as cultural factors and specific ecological conditions affecting the decision making process cannot be reproduced in lab experiments [@Janssen2015]. Therefore, this paper offers a good basis about elements influencing cooperation in commons, but future studies should confirm these results in real-life settings. Moreover, this review is not informative about the relative importance of each factor. To shed light on this topic, quantitative studies are needed.

Finally, the papers included in this review did not provide a longitudinal perspective on the study of cooperation, leaving therefore some open questions: which factors are more important in the early or in the late stages of cooperation? How the different factors evolve and influence each-others over time? To answer these questions, longitudinal investigations are needed.

In conclusion, a successful commons relies on the cooperation of its members, but this topic has not yet been extensively studied. Thus, further researches are needed to address the limitations of the current study and to reach a deeper understanding of this topic.
